---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
```


# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR] and IPUMS [@@ipumsusa]. We also follow @tellingstories how to obtain the data and analyze it. 

## How to obtain IPUMS data
In order to obtain the data from IPUMS [@@ipumsusa], first go to usa.ipums.org and then click on "Get Data" on the home page. Next click on "Select Samples", select only the 2022 ACS sample under the "USA SAMPLES" tab, and then "SUBMIT SAMPLE SELECTIONS". Then under "SELECT HARMONIZED VARIABLES" select "GEOGRAPHIC" under the "HOUSEHOLD" dropdown and choose the STATEICP variable. Under the PERSON dropdown, select EDUCATION and then the EDUC variable. After all this, click on VIEW CART on the top right and on the DATA CART Page click on "create data extract" and then on the Extract Request page make sure the data format is in the csv format. After submitting the extract on the Extract Request, create an account or log into IPUMS USA and wait for the extract to be finished and download the CSV.   

## Measurement
	
Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```



\newpage


# References


